master thesis

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - Simulation: fine tune

    The next step is to simulate the states of the nodes using the transitions. Again, fully known 
      states are simulated and then everything is 'forgotten' but a few in the leaf nodes so that 
      \colorbox{red}{you} can later compare the reconstruction with the origin. \\
    The root node is defined as ancestor of all subsequent species and in this case, determined to be
      free-living. Therefore, a beta distribution for free-living is used at the beginning. Now 
      traverse from the root to the leaf nodes, always pulling out of the current distribution until 
      the randomly drawn number is above the threshold and the new node changes state. Figure 
      \ref{fig:set node states} shows a part of this simulating states. \\
    To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
      is modeled with a beta distribution as in Figure \ref{fig:set node states}. \\

    After traversing through the tree, each state is saved in a nodelist associated with the node ID 
      which is the OTT from OTL. \\
    \begin{wrapfigure}{r}{0.65\textwidth}
      \centering
      \includegraphics[width=0.65\textwidth]{Figures/40-60_all.jpg}
      \caption{Set node states: Start with a free-living (FL) root node (red); \\
        (1) + (2) draw random numbers for its children, the numbers are under the threshold 
        $\rightarrow$ the nodes are again free-living; go on with the children; \\
        (3) draw a random number, this nubmer is over the threshold the node state changes to parasitic (P) (blue); \\
        (4) now the node states stay parasitic until the random numer lies unter the threshold.}
      \label{fig:set node states}
    \end{wrapfigure}
% simulate loss of information
    Here begins the simulation of the lost information. This is on the one hand the states and on the 
      other the topology of the tree. \\

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Implementation}
    \colorbox{red}{You} can find the full code on GitHub: 
      \hyperlink{github.com/Irallia/IZW-HU-Parasites}{github.com/Irallia/IZW-HU-Parasites}. \\
    Most of the code was written in Python. The analyzes and the use of the Castor package in R. There 
      are some shell scripts to execute whole workflows.

>>>>

    The next step is to simulate states for all nodes. \\
    The root node is defined as ancestor of all subsequent species and in this case, determined to be
      free-living. Therefore, a beta distribution for free-living is used at the beginning. Now 
      traverse from the root to the leaf nodes, always pulling out of the current distribution until 
      the randomly drawn number is above the threshold and the new node changes state. Figure 
      \ref{fig:set node states} shows a part of this simulating states. \\
    To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
      is modeled with a beta distribution as in Figure \ref{fig:set node states}. \\

    After traversing through the tree, each state is saved in a nodelist associated with the  
    \begin{wrapfigure}[21]{r}{0.65\textwidth}
      \centering
      \includegraphics[width=0.65\textwidth]{Figures/40-60_all.jpg}
      \caption{Set node states: Distribution of states (left); traversion through the tree (right). \\
        Start with a free-living root node (FL: red). \\
        (1) + (2) Draw random numbers for its children from the free-living distribution (red), the numbers are under the threshold 
        $\rightarrow$ the nodes are again free-living; go on with the children. \\
        (3) The number drawn is above the threshold. $\rightarrow$ The node state changes to parasitic (P: blue). \\
        (4) Now draw random numbers from the parasite distribution (red) until one number lies unter the threshold. Then change back.}
      \label{fig:set node states}
    \end{wrapfigure}
    node ID which is the OTT from OTL. \\

% simulate loss of information
    Here begins the simulation of the lost information. This is on the one hand the states and on the 
      other the topology of the tree. \\

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Implementation}
    The complete code is located on GitHub: 
      \hyperlink{github.com/Irallia/IZW-HU-Parasites}{github.com/Irallia/IZW-HU-Parasites}. \\
    Most of the code was written in Python. The analyzes and the use of the Castor package in R. There 
      are some shell scripts to execute whole workflows.
